%!TEX root=seke.tex
% mainfile: seke.tex

\documentclass[10pt,twocolumn]{article}

\usepackage[table]{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{latex8}
\usepackage{times}
\usepackage{inconsolata}
\usepackage{pifont}

\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}

\usepackage{tikz}
\usetikzlibrary{shapes,arrows,shadows}
\usepackage{amsmath,bm,times}
\usepackage{verbatim}

\usepackage{subcaption}
\usepackage{bibspacing}
\usepackage{fancyhdr}

%\fancypagestyle{doi}{\lfoot{DOI reference number: 10.18293/SEKE2015-205}}

\usepackage[small,compact]{titlesec}
% \usepackage{titlesec}

\pagenumbering{gobble}

\newcommand{\goallegheny}{$^{\mbox{\footnotesize \ding{72}}}$}
\newcommand{\gosheffield}{$^{\mbox{\footnotesize \ding{73}}}$}
\newcommand{\gospace}{$\;$}

% \makeatletter
% \renewenvironment{thebibliography}[1]{%
%   \vspace*{-.1in}
%   \@xp\section\@xp*\@xp{\refname}%
%   % \normalfont\footnotesize\labelsep .5em\relax
%   \renewcommand\theenumiv{\arabic{enumiv}}\let\p@enumiv\@empty
%   \vspace*{-.1in}% NEW
%   \list{\@biblabel{\theenumiv}}{\settowidth\labelwidth{\@biblabel{#1}}%
%     \leftmargin\labelwidth \advance\leftmargin\labelsep
%     \usecounter{enumiv}}%
%   % \sloppy \clubpenalty\@M \widowpenalty\clubpenalty
%   % \sfcode`\.=\@m
% }{%
%   \def\@noitemerr{\@latex@warning{Empty `thebibliography' environment}}%
%   \endlist
% }
% \makeatother

\begin{document}

% \title{Empirically Evaluating the Efficiency of Search-based \\ Test Data
% Generation for Relational Database Schemas\vspace*{-.1in}}

\title{\vspace*{-.6in}Automatically Evaluating the Efficiency of \\ Search-Based Test Data
Generation for Relational Database Schemas\vspace*{-.1in}}

\author{Cody Kinneer \goallegheny                \and
        Gregory M.\ Kapfhammer \goallegheny      \and
        Chris Wright \gosheffield                \and
        Phil McMinn \gosheffield \vspace*{-.1in}
      }

\affiliation{
      \goallegheny \gospace Allegheny College       \and
      \gosheffield \gospace University of Sheffield
}

\maketitle



\begin{abstract}
Over the years, research has explored the influence of human factors in software engineering, showing that the team members' personalities might affect teamwork. However, it is quite challenging to measure software engineers' personality due to the number of available psychometric instruments and the possibility of using different scales and classifications. Our study compares the personality traits measured by three psychometric instruments used in Software Engineering: Big Five Inventory (BFI), 16 Personality Factors (16PF), and Context Cards (CC). For this purpose, we executed an empirical study, in which we collected data from 29 software developers for each of the evaluated instruments. As a result, we identified a moderate correlation between BFI and 16PF, confirming the current state-of-the-art. For the remaining combinations, there was a weak correlation. As implications for this research, there is a need to empirically evaluate BFI and CC (context-specific survey) in terms of construct validity, since they have moderate to low correlation.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id>10002944.10011123.10011124</concept_id>
%<concept_desc>General and reference~Metrics</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}

%\ccsdesc[300]{General and reference~Software Metrics}

% We no longer use \terms command
%\terms{Theory}

\begin{IEEEkeywords} Human Aspects, Personality, Software Engineering, Psychometric Instruments, Software Team Members. \end{IEEEkeywords}

\input{1-Introduction.tex}
\input{2-Background.tex}
\input{3-Methodology.tex}
\input{4-Results.tex}
\input{5-Threats.tex}
\input{6-Conclusions.tex} 

% GMK NOTE: I removed this and moved it into the background section
% \input{writing/relatedworks}

% \titleformat{\chapter}{\huge\bf}{}{10pt}{\arabic{chapter} \ }[\titlerule]
\setlength{\bibitemsep}{.075in}
{\footnotesize
  \bibliographystyle{IEEEtran}
% \vspace*{-.05in}
\bibliography{bibtex/seke}}

\end{document}